### 2021-03-09 paper.Rmd
Putting down thoughts on my parts

@@

@@

@@

@@

>>>>

Interpolation is either between frames, or between planes
Interpolation between planes is preferred to avoid distracting effects (rotation in the plane), exception would be projection pursuit indexes that are sensitive to rotation (but that should be avoided when possible)
Geodesic interpolation uses SVD to interpolate along the shortest path between planes

XXX need to decide how much math to put in, if/which picture to use (probably something from @Buja2005-cx)

@@

Projections can hide certain features, sections can provide additional information @Furnas1994-dz
Sectioning a high-dimensional space in systematic manner is challenging, there are a lot of choices we need to make
Typical approach is interactive: brushing to select sections in one view, highlight points in a second view, e.g. a tour display
Slice tour approach: use distance from the projection plane (through a selected center point), update the section systematically with the projection plane @Laa2020-js
Summary of applications: viewing geometric shapes, model visualization
Connection with projection pursuit: section pursuit @Laa2020-ni

XXX figure should probably be combination of Fig 1 and 2 in @Laa2020-js

@@

Transformations of the data are common in the preprocessing, but sometimes we want to transform the data after projecting onto lower dimensions
Example would be to address piling effects that are a result of projecting form high-dimensional space down to low-dimensions
A solution to this problem was presented in the sage display @Laa2020-uv and is using a radial transformation of the projected data to avoid piling near the center
Summary of applications: better understanding of clustering in high-dimensional space (discussed below), resolving small features near the center

XXX I would like Fig 5 of @Laa2020-uv as an illustration here

@@

Tour for visual cluster analysis, identification of outlying points
Maybe the physics example from the ggobi book: find group in one view, highlight, restart tour, and so on, in the end we can review the tour with groups highlighted in colour to get an overview of how the data clusters
Requires persistent brushing with multiple groups

@@

Physics models often consider $\mathcal{O}(10)$ free parameters and are compared to a much larger number of experimental observables ($\mathcal{O}(100)$). The comparison typically relies on numeric computation of the model predictions for all observables, potentially obscuring the nature of their dependence on the model parameters. Here, multivariate visualisation methods can provide new insights. This was demonstrated in @Cook2018-jm. For example, we explored grouping of experiments based on how they constrain the parameter space and we also identified an interesting multivariate outlier that pointed to potential issues with the data point. For illustration we show static views from the tour showing the orthogonal structure of the three groups (indicated by color), and a display which highlights the outlyingness of the data point marked with an asterix symbol.

XXX need to select plots, also based on how much space we want to use
